%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Ajinkya Wakhale} \\ \vspace{1pt}
    Germantown, MD \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 412-499-5829 ~ \href{mailto:ajinkyawakhale3@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ajinkyawakhale3@gmail.com}} ~
    \href{https://linkedin.com/in/ajinkyawakhale}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{linkedin.com/in/ajinkyawakhale}}
    \vspace{-8pt}
\end{center}

%-----------PROFILE-----------
\section{Profile}
% BEGIN_PROFILE
\small{Principal Software Engineer with 9 years of experience leading architecture and development of large-scale distributed systems and IoT platforms. Expert in designing cloud-native microservices, implementing robust DevOps practices, and driving technical strategy across multiple product lines. Proven track record in establishing engineering best practices, mentoring development teams, and delivering high-impact solutions that improve system reliability and business outcomes.}
% END_PROFILE

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Machfu Inc}{Sep 2019 -- Present}
      {Principal Software Engineer}{Rockville, MD}
      \resumeItemListStart
        % BEGIN_DEVOPS
        \resumeItem{Architected cloud-native Java applications for provisioning, monitoring, and controlling industrial IoT assets across multiple client deployments.}
        \resumeItem{Developed Android services and field engineer applications enabling sensor communication via MQTT/HTTP to AWS and Azure backends, reducing commissioning time by 40\%.}
        \resumeItem{Built headless AOSP applications for gateway configuration, including network settings and user interfaces on custom Machfu platform.}
        \resumeItem{Led technical client engagements as primary point of contact, ensuring solution alignment with customer requirements.}
        \resumeItem{Established DevOps team and CI/CD pipeline with Jenkins, achieving 85\% build time reduction through Docker-based testing infrastructure.}
        % END_DEVOPS
        \vspace{4pt}
        \item[]
        \textit{Device Management System}
        \begin{itemize}
            % BEGIN_DEVICE_MGMT_BACKEND
            \resumeItem{Engineered multi-tenant microservice platform supporting thousands of devices, improving early issue detection by 70\%.}
            \resumeItem{Implemented event-driven architecture with MQTT pub/sub pattern using AWS IoT Shadow and Jobs, enabling bi-directional communication and real-time device state synchronization.}
            \resumeItem{Built RESTful APIs integrating device telemetry with ThingsBoard and QuickSight for real-time visualization.}
            \resumeItem{Implemented X.509 certificate-based provisioning with mutual TLS and internal PKI for secure authentication.}
            \resumeItem{Built Infrastructure as Code using AWS CDK for automated customer onboarding and provisioning.}
            \resumeItem{Architected scalable data ingestion pipeline using connection pooling and AWS service discovery for ThingsBoard integration, handling traffic spikes with minimal latency.}
            \resumeItem{Reduced AWS infrastructure costs by 40\% through strategic resource optimization, data lifecycle policies, and intelligent caching strategies.}
            % END_DEVICE_MGMT_BACKEND
        \end{itemize}
        \item[]
        \textit{Meter Diagnostics Platform}
        \begin{itemize}
            % BEGIN_METER_DIAGNOSTICS
            \resumeItem{Architected end-to-end RS-485 Modbus diagnostics platform supporting up to 32 slave devices per gateway.}
            \resumeItem{Designed self-sufficient system for air-gapped customer environment with limited remote access, incorporating comprehensive health monitoring, internal metrics, and proactive alerting to minimize intervention needs.}
            \resumeItem{Built stateless Go backend handling ~1,000 gateways with sub-second REST ingestion via in-memory caching.}
            \resumeItem{Designed horizontally scalable PostgreSQL deployment with database sharding for diagnostics persistence.}\vspace{-2pt}
            % END_METER_DIAGNOSTICS
        \end{itemize}
        \item[]
        \textit{Protocol Abstraction Framework}
        \begin{itemize}
            % BEGIN_PROTOCOL_PLATFORM
            \resumeItem{Built multithreaded Java framework abstracting Modbus and MQTT protocol complexity for rapid application development.}
            \resumeItem{Implemented AIDL and shared memory IPC with optimized serialization/deserialization pipelines.}
            \resumeItem{Created client libraries simplifying service integration across the Machfu platform.}
            % END_PROTOCOL_PLATFORM
        \end{itemize}
      \resumeItemListEnd

    \resumeSubheading
      {Comscore Inc}{Aug 2018 -- Aug 2019}
      {Automation Engineer}{Reston, VA}
      \resumeItemListStart
        % BEGIN_COMSCORE
        \resumeItem{Designed and implemented multi-node Airflow cluster with Kubernetes orchestration, automated deployment workflows using REST APIs integrating JIRA, Git, and Jenkins, and developed multi-threaded data verification modules using Python, achieving 70\% efficiency improvement in testing cycles.}
        % END_COMSCORE
      \resumeItemListEnd

    \resumeSubheading
      {Accenture}{May 2013 -- Jul 2015}
      {Software Engineer}{Bengaluru, India}
      \resumeItemListStart
        % BEGIN_ACCENTURE
        \resumeItem{Developed SAP ABAP solutions for enterprise assessment and customization tools, gaining expertise in BAPIs, RFCs, and core SAP modules including IS Banking, SD, and FICO.}
        % END_ACCENTURE
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Maryland Baltimore County}{Aug 2016 -- May 2018}
      {Master of Science in Computer Science}{Baltimore, MD}
    \resumeSubheading
      {Institute of Engineering and Technology}{Sep 2009 -- May 2013}
      {Bachelor of Engineering in Computer Engineering}{Indore, India}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, Go, C, JavaScript, Bash} \\
     \textbf{Cloud \& Infrastructure}{: AWS (IoT Core, ECS, EC2, S3, CDK, CloudWatch), Azure IoT, Docker, Kubernetes, Jenkins} \\
     \textbf{Databases}{: PostgreSQL, MySQL, DynamoDB} \\
     \textbf{IoT Protocols}{: MQTT, Modbus, BLE, DNP3} \\
     \textbf{Tools \& Frameworks}{: Spring, Flask, Maven, Gradle, JUnit, Selenium, Git, Android Studio} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}
